Abstract Binding Trees

### 2015-10-22 paper.tex
Use A_{≡} for discrete cat on set A

\newcommand\ParamsOf{\pi_\mathfrak{p}}
\newcommand\ArityOf{\pi_\mathfrak{a}}
\newcommand\Cats{\mathbf{Cat}}
\newcommand\Sets{\mathbf{Set}}
\newcommand\SCtx{\mathbf{SCtx}}

@@

Let $\Symbols$ be an infinite set of symbols. Let $\Finsets$ be the category of
finite subsets of $\Symbols$ and their injective maps; then the comma construction
$\Define{\SCtx}{\Comma{\Finsets}{\Sorts}}$, with $\Sorts$ regarded as a discrete category, is
the category of contexts of symbols, whose objects are finite sets of symbols
$U$ and sort-assignments $\mathfrak{s}:U\to\Sorts$, and whose morphisms are
sort-preserving renamings; we will write $\Upsilon$ for a symbol context
$(U,\mathfrak{s})$.

Then, fix a covariant presheaf of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Psi : C\to\Sets$ but we keep the $C$
  implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $C\Grothendieck{}{\Psi} \cong \int^{c \in C}c / C \otimes |\Psi(c)|$.}
$\Grothendieck{}{(-)} : \Sets^{C}\to\Cats$ on operators we have a category of
objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.

>>>>

\newcommand\ParamsOf{\pi_\mathfrak{p}}
\newcommand\ArityOf{\pi_\mathfrak{a}}
\newcommand\Cats{\mathbf{Cat}}
\newcommand\Discrete[1]{#1_{\equiv}}
\newcommand\Sets{\mathbf{Set}}
\newcommand\SCtx{\mathbf{SCtx}}

@@

Let $\Symbols$ be an infinite set of symbols. Let $\Finsets$ be the category of
finite subsets of $\Symbols$ and their injective maps; then the comma
construction $\Define{\SCtx}{\Comma{\Finsets}{\Discrete{\Sorts}}}$, with
$\Discrete{\Sorts}$ the discrete category on the set $\mathcal{S}$, is the
category of contexts of symbols, whose objects are finite sets of symbols $U$
and sort-assignments $\mathfrak{s}:U\to\Sorts$, and whose morphisms are
sort-preserving renamings; we will write $\Upsilon$ for a symbol context
$(U,\mathfrak{s})$.

Then, fix a covariant presheaf of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Psi : C\to\Sets$ but we keep the $C$
  implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $C\Grothendieck{}{\Psi} \cong \int^{c \in C}c / C \otimes \Discrete{\Psi(c)}$.}
$\Grothendieck{}{(-)} : \Sets^{C}\to\Cats$ on operators we have a category of
objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
